Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-30 response to reviewer.tex

\documentclass[11pt,a4paper]{{scrartcl}}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[arrow,matrix,curve]{xy}
\usepackage[latin1]{inputenc}
\usepackage{theorem}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{a4paper,top=3cm, bottom=3cm} 
\newtheorem{satz}{Theorem}
\newtheorem{aufg}[satz]{Aufgabe}
\newtheorem{defi}[satz]{Definition}
\newtheorem{bem}[satz]{Remark}
\newtheorem{kor}[satz]{Corollary}
\newtheorem{lem}[satz]{Lemma}
\newtheorem{ver}[satz]{Conjecture}
\newtheorem{zit}[satz]{Zitat}
\newtheorem{beo}[satz]{Beobachtung}
\newtheorem{bei}[satz]{Example}
\newtheorem{pro}[satz]{Proposition}
\newcommand{\dju}{\bigcup\hspace{-2.23mm\dot}\hspace{2mm}}
\newcommand{\modu}{~\rm{mod}~}
\newcommand{\smdju}{\cup\hspace{-2.15mm\dot}\hspace{2mm}}
\newcommand\dis[1]{\bigcup_{#1}\hspace{-2.5mm\dot}\hspace{2mm}}
\newcommand{\qed}{\begin{flushright}$\square$\end{flushright}}
\newcommand\R{$\mathbb{R}$}
\newcommand\Q{$\mathbb{Q}$}
\newcommand\Z{$\mathbb{Z}$}
\newcommand\N{$\mathbb{N}$}
\newcommand\C{$\mathbb{C}$}
\newcommand\Rn{\mathbb{R}}
\newcommand\Qn{\mathbb{Q}}
\newcommand\Zn{\mathbb{Z}}
\newcommand\Nn{\mathbb{N}}
\newcommand\Cn{\mathbb{C}}
\newcommand\Sk{\langle\,\,,\,\rangle}
\newcommand{\Hom}{\mathrm{Hom}}

\newcommand{\filt}[6]{
\[
\begin{xy}
\xymatrix@R20pt@C20pt{
&\mathbb{C}^3&\\\langle #1,#2 \rangle\ar[ru]&\langle #3,#4\rangle\ar[u]&\langle #5,#6\rangle\ar[lu]\\\langle #1\rangle\ar[u]&\langle #3\rangle\ar[u]&\langle #5\rangle\ar[u]}
\end{xy}
\]
}

\title{Response to the reviewer - Cell decompositions for rank two quiver Grassmannians}
\date{}

\begin{document}
\pagestyle{empty}

\maketitle

\noindent In the following, we point out the changes made and give responses to the referee's comments.

\renewcommand{\labelenumi}{(\arabic{enumi})}
\begin{enumerate}
  \item[Section 3.1:] The referee's suggestions were incorporated into shortened proofs of Lemmas 3.4, 3.15 and motivated a rewriting of the proof of Lemma 3.9.
  \item[Lemma 3.30:] The referee's comments offer a pleasing non-inductive viewpoint towards evaluating this kernel and thus have been incorporated into a new clarified proof.
  \item[Corollary 3.32:] The notation of perpendicular categories has been incorporated into the statement of the result.
  \item[Definition 3.33:] We had overlooked this simple viewpoint on admissible sequences and thank the referee for these extremely helpful remarks.
    The entire section has been somewhat reorganized to better capture the nature of the construction.
  \item[After Definition 3.33:] After the reorganization, this notation is no longer being used.
  \item[Before Lemma 3.34:] This typo has been corrected.
  \item[Lemma 3.34:] Lemma 3.34 (now 3.33) has been rewritten to clarify the inductive structure of truncated preprojectives following the change of focus onto admissible sequences.
  \item[Section 4.2:] This is a matter of convention.
    In general, the placement of the $*$'s for an attracting set is equivalent to the choice of the map $d:\{1,\ldots,n\}\to\Zn$, cells of our chosen form impose the condition $d(1)>\cdots>d(n)$.
  \item[Lemma 4.3:] We have added references to Cerulli Irelli and Haupt at the beginning of Section 4.2.
    However, Haupt's statement is stronger than his proof since it assumes a thin lift to an abelian cover, a trait our representations rarely possess.
    Furthermore, it does not seem to be straightforward to obtain our explicit description of the fixed point set of the quiver Grassmannians as those subrepresentations which live on the universal abelian covering with Haupt's construction when this applies. 
  \item[Section 4.4:] The dependence of various Caldero-Chapoton maps on their defining sequences has been clarified.
  \item[Theorem 4.20:] The proof has been reorganized and rewritten to accommodate the changes of notation surrounding admissible sequences, we hope to have clarified the proof in the process.
  \item[Theorem 4.21:] The proof has been rewritten to clarify the logic of the inductive construction by iterated torus actions.
  \item[Corollary 4.22:] We believe the proof will not be shortened much by the notational changes suggested by the referee.
    Moreover, the explicit nature of the recursion given allows one to easily construct a 2-quiver whose strong successor-closed subsets label the affine cells, Remark 4.25 has been added to alert the reader to this observation. 
\end{enumerate}

### 2019-06-30 Grassmannian_cells.tex
Theorem 4.23 and other random edits

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}

@@

The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors 
  \[\udim P_m=(u_m,u_{m-1}),\qquad\qquad \udim Q_m=(u_{m-1},u_m).\]
  These satisfy 
  \[\Hom(P_m,P_r)=0, \qquad \Hom(Q_r,Q_m)=0, \qquad \Ext(P_r,P_m)=0, \qquad \Ext(Q_m,Q_r)=0\]
  for $1\leq r\leq m$.
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $Q_m^{a_1}\oplus Q_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}

The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $Q_m$ are called \emph{preinjective}.
The following homological organization is well-known.
\begin{lemma}
  \label{le:preprojective subs}
  If $\Hom(X,P_m)\ne0$ (resp. $\Ext(P_m,X)\ne0$) for some indecomposable representation $X$ and some $m\ge1$, then $X$ must be preprojective of the form $P_r$ with $1\le r\le m$ (resp. $1\le r\le m-2$).
\end{lemma}
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  Using this, we have the following:
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad Q_1=S_2,\quad Q_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $Q_{m+1}=\tau Q_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^k M}{(\Sigma_1\Sigma_2)^k B}{(\Sigma_1\Sigma_2)^k N}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^k M}{\Sigma_2(\Sigma_1\Sigma_2)^k B}{\Sigma_2(\Sigma_1\Sigma_2)^k N}$ are exact for any $k\ge0$ and none of these representations contain preinjective direct summands.
  \end{enumerate}
\end{remark}

@@

The truncated preprojective representation $P_{m+1}^V$ has dimension vector  $\udim P_{m+1}^V=\bfd(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
These will play an important role when describing quiver Grassmannians of preprojective representations recursively.
For a dimension vector $\bfd=(d_1,d_2)\in\NN^{K(n)_0}$, write 
\[R_\bfd(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})\]
for the affine space of representations of $K(n)$ with dimension vector $\bfd$. 
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $\bfd(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The indecomposable representations of $K(n)$ with dimension vector $\bfd(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(\cH_m)$ with $\dim V=r$. 
    \item The set of indecomposable representations with dimension vector $\bfd(m,r)$ is given by a non-empty open subset of $R_{\bfd(m,r)}(K(n))$. 
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(\bfd(m,r))^\sigma=\bfd(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $\bfd(m,r)=(\ell,1)$ for $\ell:=n-r$.
  This means that $X\in R_{\bfd(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{\ell\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=\ell$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=\ell-k$.

@@

The next result establishes some basic homological properties of these translates of preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r]^{ev_I} & \tilde P_{m+1} \ar[r]^{\tilde\pi_{m+1}^I} & \tilde P_{m+1}^I \ar[r] & 0}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC\cong\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

@@

  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset \cH_m$ spanned by generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^V$ is truncated preprojective as well.
\qed\end{proof}

@@

@@

The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge2$, the following hold:
  \begin{enumerate}
    \item For $i\in\{1,\ldots,n\}$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{
           \ar[r] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[d]
          & \ar[r] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[d] \ar_{\tilde\pi_{m,i}^{\{j\}^c}}[dl] 
          & \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[d] \ar_{\tilde\pi_{m+1}^{\{i\}^c}}[dl]\\ 
          \tilde P_{m-1,(i,j)}^{\{j\}}\cong \tilde P_{m,i}^{\{j\}^c}
          & \tilde P_{m,i}^{\{i\}}\cong\tilde P_{m+1}^{\{i\}^c} \ar_(.4){\tilde\pi_{m,i}^{\{j\}^c,\{i\}}}[l] 
          & \tilde P_{m+1}^J \ar_(.4){\tilde\pi_{m+1}^{\{i\}^c,J}}[l]}
      \end{equation}
    \item For an admissible sequence $\ui\in A_1^{(k)}$, $1\le k< m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if $J\subsetneq\{i_1\}^c$ and is zero if $i_1\in J$.
    \item For any admissible word $\ui\in A_1^{(k)}$ with $0\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with~$i_k\in I$ and $i_1\notin J$ if $k\ge1$ or with $J\subsetneq I$ if $k=0$, there exist (unique up to scale) surjective maps~$\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
      These satisfy the following relations:
      \begin{itemize}
        \item $\tilde\pi_{m+1}^{\ui,I,J}\circ\tilde\pi_{m+1}^{J,K}=\tilde\pi_{m+1}^{\ui,I,K}$ for $K\subsetneq J$;
        \item $\tilde\pi_{m+1-k,\ui}^{H,I}\circ\tilde\pi_{m+1}^{\ui,I,J}=\tilde\pi_{m+1}^{\ui,H,J}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
        %\item $\tilde\pi_{m+1}^{\ui,\varnothing,I}\Big|_{\tilde P_{m+1-k,\ui}} =\tilde\pi_{m+1-k,\ui}^I$;
        %\item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $1\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
      \end{itemize}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

@@

>>>>

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}

@@

The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $Q_m$ of $K(n)$ with dimension vectors 
  \[\udim P_m=(u_m,u_{m-1}),\qquad\qquad \udim Q_m=(u_{m-1},u_m).\]
  These satisfy 
  \[\Hom(P_m,P_r)=0, \qquad \Hom(Q_r,Q_m)=0, \qquad \Ext(P_r,P_m)=0, \qquad \Ext(Q_m,Q_r)=0\]
  for $1\leq r\leq m$.
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $Q_m^{a_1}\oplus Q_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}

The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $Q_m$ are called \emph{preinjective}.
The following homological organization is well-known.
\begin{lemma}
  \label{le:preprojective subs}
  If $\Hom(X,P_m)\ne0$ (resp. $\Ext(P_m,X)\ne0$) for some indecomposable representation $X$ and some $m\ge1$, then $X$ must be preprojective of the form $P_r$ with $1\le r\le m$ (resp. $1\le r\le m-2$).
\end{lemma}
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  Using this, we have the following:
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad Q_1=S_2,\quad Q_m^\sigma=\Sigma_1 Q_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $Q_{m+1}=\tau Q_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^k M}{(\Sigma_1\Sigma_2)^k B}{(\Sigma_1\Sigma_2)^k N}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^k M}{\Sigma_2(\Sigma_1\Sigma_2)^k B}{\Sigma_2(\Sigma_1\Sigma_2)^k N}$ are exact for any $k\ge0$ and none of these representations contain preinjective direct summands.
  \end{enumerate}
\end{remark}

@@

The truncated preprojective representation $P_{m+1}^V$ has dimension vector
\[\udim P_{m+1}^V=\bfd(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m.\]
These will play an important role when describing quiver Grassmannians of preprojective representations recursively.
For a dimension vector $\bfd=(d_1,d_2)\in\NN^{K(n)_0}$, write 
\[R_\bfd(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})\]
for the affine space of representations of $K(n)$ with dimension vector $\bfd$. 
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $\bfd(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The indecomposable representations of $K(n)$ with dimension vector $\bfd(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(\cH_m)$ with $\dim V=r$. 
    \item The set of indecomposable representations with dimension vector $\bfd(m,r)$ is given by a non-empty open subset of $R_{\bfd(m,r)}(K(n))$. 
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(\bfd(m,r))^\sigma=\bfd(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $\bfd(m,r)=(\ell,1)$ for $\ell:=n-r$.
  This means that $X\in R_{\bfd(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{\ell\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=\ell$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=\ell-k$.

@@

The next result establishes some basic homological properties of these translates of preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r]^{ev_I} & \tilde P_{m+1} \ar[r]^{\tilde\pi_{m+1}^I} & \tilde P_{m+1}^I \ar[r] & 0}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)=:P_{m+1}^{\langle I\rangle}$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC\cong\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

@@

  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $\langle I\rangle\subset \cH_m$ spanned by the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_{\langle I\rangle}:P_m\otimes \langle I\rangle\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^{\langle I\rangle}$ is truncated preprojective as well.
\qed\end{proof}

@@

For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{corollary}
  \label{cor:truncated lift}
  For $m\ge1$ and $I\subsetneq\{1,\ldots,n\}$, the lift $\widetilde P_{m+1}^I$ of the truncated preprojective $P_{m+1}^{\langle I\rangle}$ is preprojective.
\end{corollary}
\begin{proof}
  We see explicitly that $\widetilde P_2^I=\Big(\prod\limits_{j\in I^c}\tilde\Sigma_{(1,\alpha_j)}\Big)(\tilde S_{(2,e)})$ is preprojective.
  The case $m\ge2$ then follows immediately from Lemma~\ref{le:truncated tau}.
\qed\end{proof}

@@

The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge2$, the following hold:
  \begin{enumerate}
    \item For $i\in\{1,\ldots,n\}$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{
           \ar[r] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[d]
          & \ar[r] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[d] \ar_{\tilde\pi_{m,i}^{\{j\}^c}}[dl] 
          & \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[d] \ar_{\tilde\pi_{m+1}^{\{i\}^c}}[dl]\\ 
          \tilde P_{m-1,(i,j)}^{\{j\}}\cong \tilde P_{m,i}^{\{j\}^c}
          & \tilde P_{m,i}^{\{i\}}\cong\tilde P_{m+1}^{\{i\}^c} \ar_(.4){\tilde\pi_{m,i}^{\{j\}^c,\{i\}}}[l] 
          & \tilde P_{m+1}^J \ar_(.4){\tilde\pi_{m+1}^{\{i\}^c,J}}[l]}
      \end{equation}
    \item For an admissible sequence $\ui\in A_1^{(k)}$, $1\le k< m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if $J\subsetneq\{i_1\}^c$ and is zero if $i_1\in J$.
    \item For any admissible word $\ui\in A_1^{(k)}$ with $0\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with~$i_k\in I$ and $i_1\notin J$ if $k\ge1$ or with $J\subsetneq I$ if $k=0$, there exist (unique up to scale) surjective maps~$\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
      These satisfy the following relations:
      \begin{itemize}
        \item $\tilde\pi_{m+1}^{\ui,I,J}\circ\tilde\pi_{m+1}^{J,K}=\tilde\pi_{m+1}^{\ui,I,K}$ for $K\subsetneq J$;
        \item $\tilde\pi_{m+1-k,\ui}^{H,I}\circ\tilde\pi_{m+1}^{\ui,I,J}=\tilde\pi_{m+1}^{\ui,H,J}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
        %\item $\tilde\pi_{m+1}^{\ui,\varnothing,I}\Big|_{\tilde P_{m+1-k,\ui}} =\tilde\pi_{m+1-k,\ui}^I$;
        %\item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $1\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
      \end{itemize}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

@@

The following result of Caldero and Reineke lays a foundation for our approach.
\begin{theorem}
  \cite{cr}
  \label{thm:smooth rigid}
  Every quiver Grassmannian of a rigid representations of an acyclic quiver is smooth.
\end{theorem}
This allows the application of the torus method of Bia\l{}ynicki-Birula described in the following section.
